raptr: Representative and Adequate Prioritisation Toolkit in R

### 2016-09-28 code/rmarkdown/article.Rmd
+  updated refs and makefile

<!-- parametrisation of biodiversity patterns and processes in conventional conservation planning tools -->
Existing conservation planning tools are generally not well-suited for representing inttra-specific biodiversity patterns and processes. To preserve the biodiversity processes that underpin a given species, a prioritisation must capture a representative sample of each species. For instance, to preserve predator-prey interactions, a prioritisation must preserve individuals from each predator and prey species in the same area. To preserve adaptive evolutionary processes, a prioritisation must preserve the adaptive landscape of each species--populations experiencing different selection pressures [@r63]. To preserve neutral evolutionary processes, a prioritisation must secure individuals descended from each of the genetic lineages that comprise each species [@r5]. Planning tools that focus on such biodiversity processes [eg. \texttt{Diversity}; @r203] are unable to accommodate species-specific targets to ensure that prioritisations secure biodiversity features. Similarly, planning tools that focus on biodiversity patterns [eg. \texttt{Marxan}] cannot easily accomodate biodiversity processes. Previous attempts to accommodate processes into multi-species conservation planning have partitioned species' ranges into different groups, for example at habitat discontinuities [e.g. @r2] as a pre-processing step to render a new set of "pseudo-species". However, this approach assumes that the biodiversity processes that operate across a species' range can be readily split into discrete units. Yet data on biodiversity processes is often continuous, hierarchical, and hyper-dimensional, and so often cannot be reduced to a few categories without significant information loss [@r218].

>>>>

<!-- parametrisation of biodiversity patterns and processes in conventional conservation planning tools -->
Existing conservation planning tools are generally not well-suited for representing intra-specific biodiversity patterns and processes. To preserve the biodiversity processes that underpin a given species, a prioritisation must capture a representative sample of each species. For instance, to preserve predator-prey interactions, a prioritisation must preserve individuals from each species in the same areas [@r471]. To preserve adaptive evolutionary processes, a prioritisation must preserve the adaptive landscape of each species--populations experiencing different selection pressures [@r63]. To preserve neutral evolutionary processes, a prioritisation must secure individuals descended from each of the genetic lineages that comprise each species [@r5]. Planning tools that focus on such biodiversity processes [eg. \texttt{Diversity}; @r203] are unable to accommodate species-specific targets to ensure that prioritisations secure biodiversity features. Similarly, planning tools that focus on biodiversity patterns [eg. \texttt{Marxan}] cannot easily accomodate biodiversity processes. Previous attempts to accommodate processes into multi-species conservation planning have partitioned species' ranges into different groups, for example at habitat discontinuities [e.g. @r2] as a pre-processing step to render a new set of "pseudo-species". However, this approach assumes that the biodiversity processes that operate across a species' range can be readily split into discrete units. Yet data on biodiversity processes is often continuous, hierarchical, and hyper-dimensional, and so often cannot be reduced to a few categories without significant information loss [@r218].
